Data-621-Project-5

### 2019-12-08 hw5/HW5_Corey.RMD

Now that we have our testing set, we will use decision trees to help us decide which variables to potentially use in our linear model.

@@

RF_with_Nulls(train,test,"TARGET",.5,10,5,.005,4,1)

@@

@@

@@

residModel2 %>% ggplot(aes(x=factor(obs), y=adjRes)) + geom_boxplot() +
  labs(title="Adjusted Residuals", subtitle="Poisson Model #2",
       x="Observed Value",y="Adjusted Residual")
```

>>>>

Now that we have our testing set, we will use decision trees to help us decide which variables to potentially use in our linear model. The first five trees look at number of cases and the last five trees look at whether or not any cases were purchased

@@

train$TARGETBOOL <- ifelse(train$TARGET > 0,1,0)
test$TARGETBOOL <- ifelse(test$TARGET>0,1,0)

RF_with_Nulls(train,test,"TARGET",.5,5,5,.005,4,1)
train %>% select(-TARGET) %>% RF_with_Nulls(test,"TARGETBOOL",.5,5,5,.005,4,1)

@@

### Try the Zero Inflated Model

```{r}
library(pscl)

model3 <- zeroinfl(TARGET ~ LabelAppeal + STARS + AcidIndex + VolatileAcidity +
                TotalSulfurDioxide + FreeSulfurDioxide + Chlorides+CitricAcid+Sulphates+ResidualSugar+pH|LabelAppeal + STARS + AcidIndex + VolatileAcidity +TotalSulfurDioxide + FreeSulfurDioxide + Chlorides+CitricAcid+Sulphates+ResidualSugar+pH, data = train, dist = "poisson")

summary(model3)

test$Prediction3 <- predict(model3, newdata=test, type="response")

cor(test$Prediction3,test$TARGET)

@@

# Model 3
residModel3 <- data.frame(obs = test$TARGET, diff = (test$TARGET - test$Prediction3))
residModel3$adjRes <- (residModel3$diff / sd(residModel3$diff))

@@

residModel2 %>% ggplot(aes(x=factor(obs), y=adjRes)) + geom_boxplot() +
  labs(title="Adjusted Residuals", subtitle="Poisson Model #2",
       x="Observed Value",y="Adjusted Residual")

residModel3 %>% ggplot(aes(x=factor(obs), y=adjRes)) + geom_boxplot() +
  labs(title="Adjusted Residuals", subtitle="Poisson Model #3",
       x="Observed Value",y="Adjusted Residual")
```
